FinalManuscript_DISCS_UG

### 2018-09-24 parts/08_appendices_a_cryptosystems.tex
Added Pailler cryptosystem description
Added initial description of the Pailler cryptosystem and explained secure homomorphic exponentiation.

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
\section{Pallier cryptosystem}
\subsection{Key generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.

Define the public key as $(g,n)$ and the private key
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2}
\end{align*}
\subsection{Homomorphic properties}
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a constant)}\\
    D(E(m_1)^{m_2}\bmod n^2)= m_1m_2\bmod n & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}
\section{Performing real number operations using integer-based cryptosystems}

>>>>

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
\section{Pallier cryptosystem}
The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
\subsection{Description}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
Define the public key as $(g,n)$ and the private key $(p,q)$.
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\subsection{Homomorphic properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
\begin{align*}
	D(E(m^k)^(m^2 \bmod n)\bmod n^2)= m^{k+2}\bmod n
\end{align*}

We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem. Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity. The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

### 2018-09-24 parts/08_appendices_b_numericalapproximations.tex
Numerical approximation integral typo
Fixed a typo in the alpha integral
Added Pailler cryptosystem description
Added initial description of the Pailler cryptosystem and explained secure homomorphic exponentiation.

%\begin{enumerate}
%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
%\item The sequence of front matter must be as follows:
%    \begin{enumerate}
%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
%    \item Abstract
%	\item Table of Contents
%	\item List of Figures
%	\item List of Tables
%	\end{enumerate}
%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
%\end{enumerate}
\chapter{NUMERICAL APPROXIMATIONS}
In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
%TODO: Include citations for this chapter
\section{Approximation for $\log(1+x)$}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align*}
This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) =
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.6\linewidth,\keepaspectratio]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}
As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{\alpha n}^{\alpha+1}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}
\section{Approximation for $x^r$}
To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
\end{align*}
This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.

>>>>

%\begin{enumerate}
%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
%\item The sequence of front matter must be as follows:
%    \begin{enumerate}
%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
%    \item Abstract
%	\item Table of Contents
%	\item List of Figures
%	\item List of Tables
%	\end{enumerate}
%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
%\end{enumerate}
\chapter{NUMERICAL APPROXIMATIONS}
Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.

We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments. In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.
.

%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
%TODO: Include citations for this chapter
\section{Approximation for $\log(1+x)$}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align*}
This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) =
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.6\linewidth,\keepaspectratio]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}
As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

\section{Approximation for $x^r$}
To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
\end{align*}
This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.
